Machine-learned embedded atom method

### 2019-08-17 doc/papers/ml-eam/manuscript.tex
Minor update.

Atomistic modeling plays a vital role in materials science. \textit{ab initio} 
calculation or force-field based molecular dynamics simulation (MD) are 
effective ways to study, understand or predict chemical and physical properties 
of materials. \textit{ab initio} approaches are generally much more precise but 
they are rarely used on large-scale metallic systems due to their extremely-high 
computation expenses. Physical model based empirical potential (force-field), 
such as the embedded-atom method (EAM), modified embedded-atom method (MEAM), 
bond-order potential (BoP), or angular-dependent potential (ADP), still plays 
the major role in long-time simulations and these empirical methods can achieve 
reasonable accuracy with much lower computation costs.

@@

Compared with empirical potentials, MILPs have some noticable advantages.

>>>>

Atomistic modeling plays a vital role in materials science. \textit{ab initio} 
calculation or force-field based molecular dynamics simulation (MD) are 
effective ways to study, understand or predict chemical and physical properties 
of materials. \textit{ab initio} approaches are generally much more precise but 
they are rarely used on large-scale metallic systems due to their extremely-high 
computation expenses. Physical model based empirical potential (force-field), 
such as the embedded-atom method (EAM), modified embedded-atom method (MEAM), 
bond-order potential (BoP), or angular-dependent potential (ADP), still plays 
the major role in long-time simulations and these empirical methods can achieve 
reasonable accuracy with much lower computation costs. Empirical potentials 
generally have very few learnable parameters and traditionally both microscopic 
observables (energy, forces, virial, etc.) and macroscopic observables (melting 
point, surface energy, etc.) can be used to tune these parameters.

@@

Compared with empirical potentials, MILPs typically have several orders of 
magnitudes more model parameters. The redundant parameter space greatly reduces 
the difficulty of fitting complicated potential energy surfaces with MLIPs. 
However, it also raises some new challenges. To effectively train MLIPs with 
large numbers of parameters, typically tens of thousands high-quality 
\textit{ab initio} data points are necessary. The cost of building training 
datasets can not be ignored. The lack of physical background makes the 
performances of MILPs outside the training 'zone' not stable. For large-scale 
alloy systems, computation efficiency becomes a major concern.
